{{< var titll >}}

### 2024-07-07 index.qmd
sumupd

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
format: 
  html:
    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
    include-in-body:
          - text: |
              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

>>>>

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
#format: 
#  html:
#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
#    include-in-body:
#          - text: |
#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)

**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

### 2024-07-07 presentation.qmd
sumupd

---
title: "Abc"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#execute: 
#  cache: false
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

ABC

>>>>

---
title: "{{< var titll >}}"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#execute: 
#  cache: false
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

# {{< var sec1.nmn >}}
# {{< var sec2.nmn >}}
# {{< var sec3.nmn >}}
# {{< var sec4.nmn >}}
# {{< var sec5.nmn >}}
# {{< var sec6.nmn >}}
# {{< var sec7.nmn >}}
# {{< var sec8.nmn >}}
# {{< var sec9.nmn >}}
